### 2023-03-12 main/chapter_2ljets.tex
add fcc etc writing

% TODO future expectations
% """
% • Sec 4.8 (Discussion): Expand on future expectations e.g. luminosities,
% heavier daughter particles with current data, HL-LHC and affect of pile-up,
% FCC etc.
% """

No end is in sight for SUSY searches, but future LHC collision data will
continue to push the high-mass frontier of sensitivity for the supersymmetric
models considered in this thesis.
% - second wave not happening
\atlas\ has published `second-wave' Run~2 papers for some similar searches,
which re-analyse the Run~2 data with refined techniques or more focussed
objectives~\cite{
ATLAS:2022hbt,
ATLAS:2022nrb
},
but the recent date of $\twoljets$'s publication suggests that \atlas\ will
use Run~3 data in its next paper on the topic.
% - Run 3 expected luminosity
% - HL-LHC
TODO~\cite{ZurbanoFernandez:2020cco}
% - If a future collider is constructed, then...

>>>>

% TODO future expectations
% """
% • Sec 4.8 (Discussion): Expand on future expectations e.g. luminosities,
% heavier daughter particles with current data,
%
% HL-LHC and affect of pile-up,
% FCC etc.
% """

No end is in sight for SUSY searches, but future LHC collision data will
continue to push the high-mass frontier of sensitivity for the supersymmetric
models considered in this thesis.
% - second wave not happening
\atlas\ has published `second-wave' Run~2 papers for some similar searches,
which re-analyse the Run~2 data with refined techniques or more focussed
objectives~\cite{ATLAS:2022hbt, ATLAS:2022nrb},
but the recent date of $\twoljets$'s publication suggests that \atlas\ will
use Run~3 data in its next paper on our topic.
% - Run 3 expected luminosity
In Run~3, the LHC is only operating at a marginally increased centre-of-mass energy
of $\sqrt{s} = 13.6\,\eV[T]$~\cite{run3sqrts};
its main benefit will therefore be the increased data quantity,
for which a a recent projection indicates a target integrated luminosity of
$250\,\mathrm{fb}^{-1}$ for proton-proton collisions by the year
2025~\cite{run3luminosity},
on top of the $139\,\mathrm{fb}^{-1}$ of Run~2.
Given similar collision conditions, this will allow sensitivity to rare signals
with proportionately small cross-sections.

% HL-LHC
Following Run~3, the LHC will be upgraded to the
High-Luminosity Large Hadron Collider (HL-LHC), whose improved operations
should yield around $300\,\mathrm{fb}^{-1}$ to $400\,\mathrm{fb}^{-1}$ of
$14\,\eV[T]$ $pp$ collisions per year.
This accelerated data rates comes at the cost of quadrupled instantaneous
luminosity (as described in Section~\ref{sec:atlas_inner}), which will push
the pile-up background from around $50$ interactions per bunch crossing in
Run~2 to around $200$ interactions per bunch crossing~\cite{
ATLAS:2022hro,
ZurbanoFernandez:2020cco
}.
The HL-LHC could yield $4000\,\mathrm{fb}^{-1}$ of proton-proton collisions,
but for corresponding sensitivity, upgrades to \atlas's hardware and software
must succeed in managing the increased pile-up background, both by
identifying pile-up events and by modelling them in simulation.

Collision energies ultimately bound the masses of heavy particles that can
be produced in collisions, so stronger accelerators will be necessary
to expand the search in that direction.
Future prospects for the coming decades at CERN include the
High-Energy LHC (HE-LHC), which could achieve $\sqrt{s}=27\,\eV[T]$ with new
hardware in the current LHC tunnel~\cite{FCC:2018byv},
and a Future Circular Collider (FCC), whose new $100\,\mathrm{km}$
`quasi-circular' tunnel would permit proton collisions at
$\sqrt{s}=100\,\eV[T]$~\cite{FCC:2018vvp}.
Just as the LHC follows the LEP electron-positron collider, this FCC hadron
collider (FCC-hh) might be proceeded by an electron-positron collider (FCC-ee)
with centre-of-mass energies high enough (up to $\sqrt{s}=350\,\eV[T]$) to
pair-produce all Standard Model particles~\cite{FCC:2018evy}.
Such scrutiny of the Standard Model is also a search for new physical effects,
and including some that could be explained with supersymmetric
models~\cite{FCC:2018byv, Gounaris1999}.
